Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-17 WSSSPE2_report/WSSSPE2_review.tex
Use inter-word space after middle initials
minor change in wording
Add name to contributors list
Add line breaks.
Use short url for TODO. Fix typos.

link to live notes - \url{https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing}

The Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2)\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe2/}} was held on Sunday, 16 November 2014 in conjunction with the 2014 International Conference for High Performance Computing, Networking, Storage and Analysis (SC14)\footnote{\url{http://sc14.supercomputing.org}}.
WSSSPE2 followed a general initial workshop, WSSSPE1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe1/}}~\cite{WSSSPE1-pre-report,WSSSPE1}, that was held in 2013 in conjunction with the SC13 conference, and a focused workshop, WSSSPE1.1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe1-1/}}, that was held in 2014 in conjunction with the SciPy conference.

Progress in scientific research is dependent on the quality and accessibility of software at all levels and it is critical to address challenges related to the development, deployment, maintenance and overall sustainability of reusable software as well as education around software practices. These challenges can be technological, policy based, organizational, and educational, and are of interest to developers (the software community), users (science disciplines), software engineering researchers, and researchers studying the conduct of science (science of team science, science of organizations, science of science and innovation policy, and social science communities). The WSSSPE1 workshop engaged the broad scientific community to identify challenges and best practices in areas of interest for sustainable scientific software. WSSSPE2 invites the community to propose and discuss specific mechanisms to move towards an imagined future practice for software development and usage in science and engineering. The workshop will include multiple mechanisms for participation, encourage team building around solutions, and identify risky solutions with potentially transformative outcomes. Participation by early career students and postdoctoral researchers is strongly encouraged.

>>>>

link to live notes -
\url{tinyurl.com/q6ew45v}%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing}

The Second Workshop on Sustainable Software for Science: Practice and
Experiences
(WSSSPE2)\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe2/}} was
held on Sunday, 16 November 2014 in conjunction with the 2014 International
Conference for High Performance Computing, Networking, Storage and Analysis
(SC14)\footnote{\url{http://sc14.supercomputing.org}}.
WSSSPE2 followed a general initial workshop,
WSSSPE1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe1/}}~\cite{WSSSPE1-pre-report,WSSSPE1},
that was held in 2013 in conjunction with the SC13 conference, and a focused
workshop,
WSSSPE1.1\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe1-1/}},
that was held in 2014 in conjunction with the SciPy conference.

Progress in scientific research is dependent on the quality and accessibility of
software at all levels and it is critical to address challenges related to the
development, deployment, maintenance, and overall sustainability of reusable
software as well as education around software practices. These challenges can be
technological, policy based, organizational, and educational, and are of
interest to developers (the software community), users (science disciplines),
software-engineering researchers, and researchers studying the conduct of
science (science of team science, science of organizations, science of science
and innovation policy, and social science communities). The WSSSPE1 workshop
engaged the broad scientific community to identify challenges and best practices
in areas of interest for sustainable scientific software. WSSSPE2 invites the
community to propose and discuss specific mechanisms to move towards an imagined
future practice for software development and usage in science and engineering.
The workshop includes multiple mechanisms for participation, encourages team
building around solutions, and identifies risky solutions with potentially
transformative outcomes. It strongly encourages participation of early-career
students and postdoctoral researchers.
